A Spiking Independent Accumulator Model for\\Winner-Take-All Computation

### 2017-07-21 doc/poster/poster.tex
Fix overfull hbox in poster.
Add IA abbreviation to poster.
Update poster with meeting feedback.

        \begin{tcolorbox}[adjusted title=Benchmarks, add to width=-3cm]

@@

                \item Ability to provide a clear output (single output above \num{0.15}, stable over at least \SI{1}{\second})
                \item Correctness (output corresponds to strongest input)
                \item Time required to reach a decision
                \item Transient outputs before final decision is reached

@@

            \begin{minipage}[c][6in]{20cm}

@@

@@

        \begin{tcolorbox}[raster multicolumn=4,title=Independent Accumulators,halign title=left]
            \begin{minipage}[c]{20cm}

@@

>>>>

        \begin{tcolorbox}[adjusted title=Definitions, add to width=-3cm]

@@

                \item \textbf{Clear:} single output above \num{0.15}, stable over at least  \SI{1}{\second}
                \item \textbf{Correct:} output corresponds to strongest input
                \item \textbf{Input magnitude:} Magnitude of target input
                \item \textbf{Target separation:} Separation of target input from non-target inputs 

@@

            \begin{minipage}[c][6in]{21.5cm}

@@

            \raisebox{-0.5\height}{\includegraphics[trim=0 0 0 80]{lca-example}}
            \hspace{1.5cm}

@@

        \begin{tcolorbox}[raster multicolumn=4,title=Independent Accumulators (IA),halign title=left]
            \begin{minipage}[c]{21.5cm}

@@

            \raisebox{-0.5\height}{\includegraphics[trim=0 0 0 80]{ia-example}}
            \hspace{1.5cm}
